Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2022-02-07 Thesis/01-chap1.Rmd
add introduction part

Based on the answer to the above questions, four major approaches to pursue AI have been established. They can be summarized into a two by two table as shown in figure \@ref(fig:twodimai), where the row is "Human" vs "Rational", and the column is "Behaviour" vs "Thought". Positioning at the top right cell, the **rational agent approach** aims to build agent that perform mathematically perfect acts such that the best expected outcome can always be achieved. In contrast, the **"laws of thought" approach** focus on understanding the logic behind the rationality. Closely related to **cognitive science**, the **cognitive modelling approach** attempts to express theories of human cognition as computer program to mimic the thought process of human. Lastly, the **Turing test approach** is built upon the famous **Turing test** proposed by @turing_computing_1950. The test can be roughly described as, whether a human can distinguish another human from a computer with written communications only. To pass the test, several capabilities of computer are required. This includes **natural language processing**, **knowledge representation**, **automated reasoning** and **machine learning**. Some researchers argued that some degree of physical simulation of a person is still necessary, one such example is the **total Turing test** proposed by @harnad_other_1991. It adds new requirements to the list, including **computer vision**, **speech recognition** and **robotics** [@russell_artificial_2002].

Notably, all $6$ required capabilities have become major subfields of AI today.

Among The most influential one may be the machine learning, which highly rely on the predictive modelling framework.

Donoho (2017) in its summary of data science stated that the concept of this modelling culture could be traced back to an article written by Breiman (2001). In contrast to the generative modelling culture, which aims to develop stochastic models to make inferences about the data generating process, predictive modelling emphasizes the ability of the model to make accurate predictions.

Behind the success of AI and computer vision, a great proportion of their applications highly rely on the predictive modelling framework.

>>>>

Based on the answer to the above questions, four major approaches to pursue AI have been established. They can be summarized into a two by two table as shown in figure \@ref(fig:twodimai), where the row is "Human" vs "Rational", and the column is "Behaviour" vs "Thought". Positioning at the top right cell, the **rational agent approach** aims to build agent that perform mathematically perfect acts such that the best expected outcome can always be achieved. In contrast, the **"laws of thought" approach** focus on understanding the logic behind the rationality. Closely related to **cognitive science**, the **cognitive modelling approach** attempts to express theories of human cognition as computer program to mimic the thought process of human. Lastly, the **Turing test approach** is built upon the famous **Turing test** proposed by @turing_computing_1950. The test can be roughly described as, whether a human can distinguish another human from a computer with written communications only. To pass the test, several capabilities of computer are required. This includes **natural language processing**, **knowledge representation**, **automated reasoning** and **machine learning**. Some researchers argued that some degree of physical simulation of a person is still necessary, one such example is the **total Turing test** proposed by @harnad_other_1991. It adds new requirements to the list, including **computer vision**, **speech recognition** and **robotics** [@russell_artificial_2002]. As of today, all $7$ required capabilities have become major subfields of AI.

Notably, machine learning, acts as the core of AI, has been developed rapidly in recent years thanks for the big-data era and the accessible and low-cost computational power [@jordan_machine_2015]. It is a field of study addresses the issues of building computers that can adapt to new circumstances automatically through experience and data. Machine learning applications such as facial recognition, web recommendation system and machine translation have a significant impact on human's daily life. Behind the success of machine learning, a great propotion of its applications rely on the predictive modelling framework. Donoho (2017) in its summary of data science stated that the concept of this modelling culture could be traced back to an article written by Breiman (2001). In contrast to the generative modelling culture, which aims to develop stochastic models to make inferences about the data generating process, predictive modelling emphasizes the ability of the model to make accurate predictions.
